Graph Databases for Use with Timeseries IoT Datasets

### 2023-12-01 paper.tex
Final Paper Close to Finished
The final paper is close to finish

@@

@@

@@

\section{Conclusion}

>>>>

With the question of network scans out of the way, the last question remained.
Was it possible that any of the sinks were being DDoSed?
For a DDoS to occur there should be an odd number of incoming, unique, flows to a particular IP address.

@@

As shown in figure \ref{fig:incomingflows} there is no evidence that any DDoS attacks occured withing this timeframe,
ruling out a DDoS attack as a source of the flows to the IoT device.

@@

Clearly the work done here is just the beginning, however the results already gained show great promise of revealing
important information. From so little data and simple queries we can already determine whether two important attacks
occur. However the results found by these queries on this dataset are limited. For one, only simple queries were
and more advanced queries could and should be used in the future in order to solve more complicated problems and
answer more complicated questions. Secondly, the fraction of the dataset used only involved 1,000,000 flows. In
order to get a more accurate picture of a network, millions more flows so be gathered and analyzed. Luckily,
due to the speed of graph databases, this shouldn't be a problem for similar experiments in the future.

@@

The work in this paper should be considered a beginning rather than an end. There are so many doors and paths
the author was not able to take during this project due to various limitations and constraints. Work for both
the author and readers for the future include, but are not limited to, expanding the queries performed to answer
more complicated questions. In addition, additional work should be done to analyze these basic questions at scale,
whether that be scale of time or scale of data. More work also needs to be performed on the comparison of the
utility of graph databases for these tasks in comparison to more traditional methods as well as the benefits
and/or downfalls to increasing efficiency of the existing systems for these tasks.

\section{Conclusion}
Graph databases proved to be a useful tool for IoT device timeseries data. It is both fast to query and the
information gained provide meaningful answers to interesting questions.
